sem

### 2022-12-07 scripts/workshop/sem.Rmd
Update sem.Rmd

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- glm(cc ~ MeanWaterTempPredC, data = comm_data)
size_temp <- glm(size ~ MeanWaterTempPredC, data = comm_data)
prev_cc <- glm(Prevalence ~ cc + size, data = comm_data)

@@

```{r}
summary(sem)
```

>>>>

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- glm(cc ~ MeanWaterTempPredC, data = comm_data)
size_temp <- glm(size ~ MeanWaterTempPredC, data = comm_data)
prev_cc <- glm(Prevalence ~ cc + MeanWaterTempPredC + size, data = comm_data)

@@

```{r}
dSep(sem)
summary(sem)
```
